### 2014-03-09 docs/paper.tex
Some notes on CloudFlare.

>>>>

\section{Other third-party services}

A censor can block meek by blocking access to Google entirely.
To take such a step is extreme, because of its high collateral damage,
but it is not outside the realm of possibility.
% Cite when Google and Gmail were completely blocked temporarily.
We investigated how easily our system can be adapted to hard-to-block systems other than Google,
and found that CloudFlare, a content delivery network, in principle supports domain fronting.

CloudFlare provides the frontend of $X$ web sites, $Y$ of them supporting HTTPS~\cite{something}.
CloudFlare supports the domain fronting trick;
that is, it is possible that a request has one domain in the TLS layer
and another in the HTTP layer, and the CloudFlare server will transparently redirect it to proper place.
While we verified that domain fronting would work on CloudFlare,
we did not test deployment,
because when we asked we were told that our planned use would be against CloudFlare's terms of service.
CloudFlare hosts a number of HTTPS sites.
Choosing just one of them to be the front in TLS connections could cause
the innocent third-party domain to be censored even though it is not itself carrying any circumvention traffic.
To avoid this problem, the front can be simply a CloudFlare IP address,
with no SNI at all.
The censor then faces the choice of allowing circumvention traffic,
or else blocking a large number of popular unrelated web sites.

We were not able to make the system work with Amazon CloudFront nor Akamai.
